|

### 2016-05-25 Benchmark/MSGF-Benchmark/msgf-benchmark.Rmd
benchmark

# 6. Filtering (Docker --> PNNL)

```{r include=F}
evalue = 1e-10
```

# a Spec-Evalue `r evalue`
### From PNNL
```{r, echo =F}
pnnl_tmp <- pnnl[pnnl$MSGFDB_SpecEValue<evalue,]
print("==Head==")
head(pnnl_tmp,2)
print("==Tail==")
tail(pnnl_tmp,2)
```
There are ```r nrow(pnnl_tmp)``` rows remained.

### From Docker 
```{r echo=F}
tmp <- (p3_table[p3_table$'ms-gf:specevalue'<evalue & !is.na(p3_table$'ms-gf:specevalue'<evalue),c("scan number(s)", "ms-gf:specevalue", "pepseq")])
tmp <- tmp[order(tmp$`ms-gf:specevalue`),]
print("==Head==")
head(tmp,2)
print("==Tail==")
tail(tmp,2)

bt_tmp <- merge(x =  tmp, y=pnnl, by.y = "Scan", by.x  =  "scan number(s)", all.x = T)
bt_tmp <- bt_tmp[order(bt_tmp$`ms-gf:specevalue`, decreasing = F),]
tmp_nona <- bt_tmp[is.na(bt_tmp$MSGFDB_SpecEValue),]
tmp_nona <- tmp_nona[order(tmp_nona$'ms-gf:specevalue', decreasing = F),]
bt_tmp <- bt_tmp[!is.na(bt_tmp$Peptide),]
```
There are ```r nrow(tmp)``` rows remained.

### Differences
Data from Docker is matched with from PNNL using scan number as ID. `r names(bt_tmp)[2:3]` are values from Docker. `r names(bt_tmp)[4:5]` are the corresponding values from PNNL. There are `r nrow(bt_tmp)` of rows in total with  `r nrow(bt_tmp[((bt_tmp$'ms-gf:specevalue'==bt_tmp$MSGFDB_SpecEValue) & (bt_tmp$pepseq==bt_tmp$Peptide)),])` exact match.

Aside from the `r nrow(tmp_nona)` unmatched values, `r sum(bt_tmp$'ms-gf:specevalue'!=bt_tmp$MSGFDB_SpecEValue)` have different spec-evalue, `r sum(bt_tmp$pepseq!=bt_tmp$Peptide)` of different peptide identification.

```{r echo=F}
print("==Head==")
head(bt_tmp,2)
print("==Tail==")
tail(bt_tmp,2)

print("==Unmatched==")
head(tmp_nona,2)
print("==Different Spec Values==")
head(bt_tmp[(bt_tmp$'ms-gf:specevalue'!=bt_tmp$MSGFDB_SpecEValue),],2)
print("==Different Peptides identification==")
head(bt_tmp[(bt_tmp$pepseq!=bt_tmp$Peptide),],2)

@@

```{r include=F}
evalue = 1e-15
```

# b. Spec-Evalue `r evalue`
### From PNNL
```{r, echo =F}
pnnl_tmp <- pnnl[pnnl$MSGFDB_SpecEValue<evalue,]
print("==Head==")
head(pnnl_tmp,2)
print("==Tail==")
tail(pnnl_tmp,2)
```
There are ```r nrow(pnnl_tmp)``` rows remained.

### From Docker 
```{r echo=F}
tmp <- (p3_table[p3_table$'ms-gf:specevalue'<evalue & !is.na(p3_table$'ms-gf:specevalue'<evalue),c("scan number(s)", "ms-gf:specevalue", "pepseq")])
tmp <- tmp[order(tmp$`ms-gf:specevalue`),]
print("==Head==")
head(tmp,2)
print("==Tail==")
tail(tmp,2)

bt_tmp <- merge(x =  tmp, y=pnnl, by.y = "Scan", by.x  =  "scan number(s)", all.x = T)
bt_tmp <- bt_tmp[order(bt_tmp$`ms-gf:specevalue`, decreasing = F),]
tmp_nona <- bt_tmp[is.na(bt_tmp$MSGFDB_SpecEValue),]
tmp_nona <- tmp_nona[order(tmp_nona$'ms-gf:specevalue', decreasing = F),]
bt_tmp <- bt_tmp[!is.na(bt_tmp$Peptide),]
```
There are ```r nrow(tmp)``` rows remained.

### Differences
Data from Docker is matched with from PNNL using scan number as ID. `r names(bt_tmp)[2:3]` are values from Docker. `r names(bt_tmp)[4:5]` are the corresponding values from PNNL. There are `r nrow(bt_tmp)` of rows in total with  `r nrow(bt_tmp[((bt_tmp$'ms-gf:specevalue'==bt_tmp$MSGFDB_SpecEValue) & (bt_tmp$pepseq==bt_tmp$Peptide)),])` exact match.

Aside from the `r nrow(tmp_nona)` unmatched values, `r sum(bt_tmp$'ms-gf:specevalue'!=bt_tmp$MSGFDB_SpecEValue)` have different spec-evalue, `r sum(bt_tmp$pepseq!=bt_tmp$Peptide)` of different peptide identification.

```{r echo=F}
print("==Head==")
head(bt_tmp,2)
print("==Tail==")
tail(bt_tmp,2)

print("==Unmatched==")
head(tmp_nona,2)
print("==Different Spec Values==")
head(bt_tmp[(bt_tmp$'ms-gf:specevalue'!=bt_tmp$MSGFDB_SpecEValue),],2)
print("==Different Peptides identification==")
head(bt_tmp[(bt_tmp$pepseq!=bt_tmp$Peptide),],2)

```{r include=F}
evalue = 1e-20
```

# c. Spec-Evalue `r evalue`
### From PNNL
```{r, echo =F}
pnnl_tmp <- pnnl[pnnl$MSGFDB_SpecEValue<evalue,]
print("==Head==")
head(pnnl_tmp,2)
print("==Tail==")
tail(pnnl_tmp,2)
```
There are ```r nrow(pnnl_tmp)``` rows remained.

### From Docker 
```{r echo=F}
tmp <- (p3_table[p3_table$'ms-gf:specevalue'<evalue & !is.na(p3_table$'ms-gf:specevalue'<evalue),c("scan number(s)", "ms-gf:specevalue", "pepseq")])
tmp <- tmp[order(tmp$`ms-gf:specevalue`),]
print("==Head==")
head(tmp,2)
print("==Tail==")
tail(tmp,2)

bt_tmp <- merge(x =  tmp, y=pnnl, by.y = "Scan", by.x  =  "scan number(s)", all.x = T)
bt_tmp <- bt_tmp[order(bt_tmp$`ms-gf:specevalue`, decreasing = F),]
tmp_nona <- bt_tmp[is.na(bt_tmp$MSGFDB_SpecEValue),]
tmp_nona <- tmp_nona[order(tmp_nona$'ms-gf:specevalue', decreasing = F),]
bt_tmp <- bt_tmp[!is.na(bt_tmp$Peptide),]
```
There are ```r nrow(tmp)``` rows remained.

### Differences
Data from Docker is matched with from PNNL using scan number as ID. `r names(bt_tmp)[2:3]` are values from Docker. `r names(bt_tmp)[4:5]` are the corresponding values from PNNL. There are `r nrow(bt_tmp)` of rows in total with  `r nrow(bt_tmp[((bt_tmp$'ms-gf:specevalue'==bt_tmp$MSGFDB_SpecEValue) & (bt_tmp$pepseq==bt_tmp$Peptide)),])` exact match.

Aside from the `r nrow(tmp_nona)` unmatched values, `r sum(bt_tmp$'ms-gf:specevalue'!=bt_tmp$MSGFDB_SpecEValue)` have different spec-evalue, `r sum(bt_tmp$pepseq!=bt_tmp$Peptide)` of different peptide identification.

```{r echo=F}
print("==Head==")
head(bt_tmp,2)
print("==Tail==")
tail(bt_tmp,2)

print("==Unmatched==")
head(tmp_nona,2)
print("==Different Spec Values==")
head(bt_tmp[(bt_tmp$'ms-gf:specevalue'!=bt_tmp$MSGFDB_SpecEValue),],2)
print("==Different Peptides identification==")
head(bt_tmp[(bt_tmp$pepseq!=bt_tmp$Peptide),],2)

```{r include=F}
evalue = 1e-15
```

```{r include=F}
evalue = 1e-10
```

# a. Spec-Evalue `r evalue`
### From PNNL
```{r, echo =F}
pnnl_tmp <- pnnl[pnnl$MSGFDB_SpecEValue<evalue,]
print("==Head==")
head(pnnl_tmp,2)
print("==Tail==")
tail(pnnl_tmp,2)
```
There are ```r nrow(pnnl_tmp)``` rows remained.

### From Docker 
```{r echo=F}
tmp <- (p3_table[p3_table$'ms-gf:specevalue'<evalue & !is.na(p3_table$'ms-gf:specevalue'<evalue),c("scan number(s)", "ms-gf:specevalue", "pepseq")])
tmp <- tmp[order(tmp$`ms-gf:specevalue`),]
print("==Head==")
head(tmp,2)
print("==Tail==")
tail(tmp,2)

bt_tmp <- merge.data.frame(y =  p3_table[,c("scan number(s)", "ms-gf:specevalue", "pepseq")], x=pnnl_tmp, by.x = "Scan", by.y  =  "scan number(s)", all.x = T, all.y = F)
bt_tmp <- bt_tmp[order(bt_tmp$`ms-gf:specevalue`, decreasing = F),]
tmp_nona <- bt_tmp[is.na(bt_tmp$'ms-gf:specevalue'),]
tmp_nona <- tmp_nona[order(tmp_nona$MSGFDB_SpecEValue, decreasing = F),]
bt_tmp <- bt_tmp[!is.na(bt_tmp$'pepseq'),]
```
There are ```r nrow(tmp)``` rows remained.

### Differences
Data from Docker is matched with from PNNL using scan number as ID. `r names(bt_tmp)[2:3]` are values from PNNL. `r names(bt_tmp)[4:5]` are the corresponding values from Docker Container. There are `r nrow(bt_tmp)` of rows in total with   `r nrow(bt_tmp[((bt_tmp$'ms-gf:specevalue'==bt_tmp$MSGFDB_SpecEValue) & (bt_tmp$pepseq==bt_tmp$Peptide)),])` exact match.

Aside from the `r nrow(tmp_nona)` unmatched values, `r sum(bt_tmp$'ms-gf:specevalue'!=bt_tmp$MSGFDB_SpecEValue)` have different spec-evalue, `r sum(bt_tmp$pepseq!=bt_tmp$Peptide)` of different peptide identification.

```{r echo=F}
print("==Head==")
head(bt_tmp,2)
print("==Unmatched==")
head(tmp_nona,3)
print("==Tail==")
tail(bt_tmp,2)

print("==Unmatched==")
head(tmp_nona,2)
print("==Different Spec Values==")
head(bt_tmp[(bt_tmp$'ms-gf:specevalue'!=bt_tmp$MSGFDB_SpecEValue),],2)
print("==Different Peptides identification==")
head(bt_tmp[(bt_tmp$pepseq!=bt_tmp$Peptide),],2)

```{r include=F}
evalue = 1e-15
```

# b. Spec-Evalue `r evalue`

### From PNNL
```{r, echo =F}
pnnl_tmp <- pnnl[pnnl$MSGFDB_SpecEValue<evalue,]
head(pnnl_tmp,2)
tail(pnnl_tmp,2)
```
There are ```r nrow(pnnl_tmp)``` rows remained.

### From Docker 
```{r echo=F}
tmp <- (p3_table[p3_table$'ms-gf:specevalue'<evalue & !is.na(p3_table$'ms-gf:specevalue'<evalue),c("scan number(s)", "ms-gf:specevalue", "pepseq")])
tmp <- tmp[order(tmp$`ms-gf:specevalue`),]
print("==Head==")
head(tmp,2)
print("==Tail==")
tail(tmp,2)

bt_tmp <- merge.data.frame(y =  p3_table[,c("scan number(s)", "ms-gf:specevalue", "pepseq")], x=pnnl_tmp, by.x = "Scan", by.y  =  "scan number(s)", all.x = T, all.y = F)
bt_tmp <- bt_tmp[order(bt_tmp$`ms-gf:specevalue`, decreasing = F),]
tmp_nona <- bt_tmp[is.na(bt_tmp$'ms-gf:specevalue'),]
tmp_nona <- tmp_nona[order(tmp_nona$MSGFDB_SpecEValue, decreasing = F),]
bt_tmp <- bt_tmp[!is.na(bt_tmp$'pepseq'),]
```
There are ```r nrow(tmp)``` rows remained.

### Differences
Data from Docker is matched with from PNNL using scan number as ID. `r names(bt_tmp)[2:3]` are values from PNNL. `r names(bt_tmp)[4:5]` are the corresponding values from Docker Container. There are `r nrow(bt_tmp)` of rows in total with   `r nrow(bt_tmp[((bt_tmp$'ms-gf:specevalue'==bt_tmp$MSGFDB_SpecEValue) & (bt_tmp$pepseq==bt_tmp$Peptide)),])` exact match.

Aside from the `r nrow(tmp_nona)` unmatched values, `r sum(bt_tmp$'ms-gf:specevalue'!=bt_tmp$MSGFDB_SpecEValue)` have different spec-evalue, `r sum(bt_tmp$pepseq!=bt_tmp$Peptide)` of different peptide identification.

```{r echo=F}
print("==Head==")
head(bt_tmp,2)
print("==Unmatched==")
head(tmp_nona,3)
print("==Tail==")
tail(bt_tmp,2)

print("==Unmatched==")
head(tmp_nona,2)
print("==Different Spec Values==")
head(bt_tmp[(bt_tmp$'ms-gf:specevalue'!=bt_tmp$MSGFDB_SpecEValue),],2)
print("==Different Peptides identification==")
head(bt_tmp[(bt_tmp$pepseq!=bt_tmp$Peptide),],2)

```{r include=F}
evalue = 1e-20
```

# c. Spec-Evalue `r evalue`

### From PNNL
```{r, echo =F}
pnnl_tmp <- pnnl[pnnl$MSGFDB_SpecEValue<evalue,]
head(pnnl_tmp,2)
tail(pnnl_tmp,2)
```
There are ```r nrow(pnnl_tmp)``` rows remained.

### From Docker 
```{r echo=F}
tmp <- (p3_table[p3_table$'ms-gf:specevalue'<evalue & !is.na(p3_table$'ms-gf:specevalue'<evalue),c("scan number(s)", "ms-gf:specevalue", "pepseq")])
tmp <- tmp[order(tmp$`ms-gf:specevalue`),]
print("==Head==")
head(tmp,2)
print("==Tail==")
tail(tmp,2)

bt_tmp <- merge.data.frame(y =  p3_table[,c("scan number(s)", "ms-gf:specevalue", "pepseq")], x=pnnl_tmp, by.x = "Scan", by.y  =  "scan number(s)", all.x = T, all.y = F)
bt_tmp <- bt_tmp[order(bt_tmp$`ms-gf:specevalue`, decreasing = F),]
tmp_nona <- bt_tmp[is.na(bt_tmp$'ms-gf:specevalue'),]
tmp_nona <- tmp_nona[order(tmp_nona$MSGFDB_SpecEValue, decreasing = F),]
bt_tmp <- bt_tmp[!is.na(bt_tmp$'pepseq'),]
```
There are ```r nrow(tmp)``` rows remained.

### Differences
Data from Docker is matched with from PNNL using scan number as ID. `r names(bt_tmp)[2:3]` are values from PNNL. `r names(bt_tmp)[4:5]` are the corresponding values from Docker Container. There are `r nrow(bt_tmp)` of rows in total with   `r nrow(bt_tmp[((bt_tmp$'ms-gf:specevalue'==bt_tmp$MSGFDB_SpecEValue) & (bt_tmp$pepseq==bt_tmp$Peptide)),])` exact match.

Aside from the `r nrow(tmp_nona)` unmatched values, `r sum(bt_tmp$'ms-gf:specevalue'!=bt_tmp$MSGFDB_SpecEValue)` have different spec-evalue, `r sum(bt_tmp$pepseq!=bt_tmp$Peptide)` of different peptide identification.

```{r echo=F}
print("==Head==")
head(bt_tmp,2)
print("==Unmatched==")
head(tmp_nona,3)
print("==Tail==")
tail(bt_tmp,2)

print("==Unmatched==")
head(tmp_nona,2)
print("==Different Spec Values==")
head(bt_tmp[(bt_tmp$'ms-gf:specevalue'!=bt_tmp$MSGFDB_SpecEValue),],2)
print("==Different Peptides identification==")
head(bt_tmp[(bt_tmp$pepseq!=bt_tmp$Peptide),],2)

>>>>

```{r no 7, echo=F}
############# 7##########################
evalue = 1e-10
```

# a. Spec-Evalue `r evalue`
### From PNNL
```{r, echo =F}
pnnl_tmp <- pnnl[pnnl$MSGFDB_SpecEValue<evalue,]
```
There are ```r nrow(pnnl_tmp)``` rows remained.

### From Docker 
```{r echo=F}
tmp <- (p3_table[p3_table$'ms-gf:specevalue'<evalue & !is.na(p3_table$'ms-gf:specevalue'<evalue),c("scan number(s)", "ms-gf:specevalue", "pepseq")])
tmp <- tmp[order(tmp$`ms-gf:specevalue`),]

bt_tmp <- merge.data.frame(y =  p3_table[,c("scan number(s)", "ms-gf:specevalue", "pepseq")], x=pnnl_tmp, by.x = "Scan", by.y  =  "scan number(s)", all.x = T, all.y = F)
bt_tmp <- bt_tmp[order(bt_tmp$`ms-gf:specevalue`, decreasing = F),]
tmp_nona <- bt_tmp[is.na(bt_tmp$'ms-gf:specevalue'),]
tmp_nona <- tmp_nona[order(tmp_nona$MSGFDB_SpecEValue, decreasing = F),]
bt_tmp <- bt_tmp[!is.na(bt_tmp$'pepseq'),]
the_x = bt_tmp[((bt_tmp$'ms-gf:specevalue'==bt_tmp$MSGFDB_SpecEValue) & (bt_tmp$pepseq==bt_tmp$Peptide)),]
the_y = bt_tmp[((bt_tmp$'ms-gf:specevalue'!=bt_tmp$MSGFDB_SpecEValue) & (bt_tmp$pepseq==bt_tmp$Peptide)),]
the_z = bt_tmp[((bt_tmp$'ms-gf:specevalue'!=bt_tmp$MSGFDB_SpecEValue) & (bt_tmp$pepseq!=bt_tmp$Peptide)),]

```
There are ```r nrow(tmp)``` rows remained.

```{r echo=F}
print("==Head==")
head(bt_tmp,2)
print("==Tail==")
tail(bt_tmp,2)
```

### Differences
Data from Docker is matched with from PNNL using scan number as ID. `r names(bt_tmp)[2:3]` are values from PNNL. `r names(bt_tmp)[4:5]` are the corresponding values from Docker Container. There are `r nrow(bt_tmp)` of rows in total with   `r nrow(the_x)` exact match.

Aside from the `r nrow(tmp_nona)` unmatched values, `r nrow(the_y)` with the same peptide identification and different spec-evalue, `r nrow(the_z)` of different peptide identification as well different spec-evalues.

```{r echo=F}
print("==Unmatched==")
head(tmp_nona,2)
print("==Different Spec eValues==")
head(the_y,2)
print("==Different Peptides identification and different Spec Evalues==")
head(the_z,2)

@@
